---
title: "week2"
author: "Marcelle"
date: "1/27/2022"
output: html_document
---


#R-markdown differs from script because when it converts text to HTML it is rendered nicely, including the R code such as an embedded plot
#you can edit HTML page later on as well

#byrow argument: FALSE will fill columns firsy (the default)
#TRUE will fill rows first
#Array are n-dimensional data structures
#attributes include dim(a), class(a), attributes(a), str(a)
#reminder: str(a) is structure

#subsetting using index positions() and bracket notation([])
#index positions: extract depending on position 
#example: m[1,1] will pull from (row, column)
#list and Data Frames 
```{r}
s <- c("this", "is", "a", "vector", "of", "strings")
```
#double bracket is a matrix: will extract as an object with attributes of a e.i. matrix
#single bracket returns a list: used to subset elements out of a list

#data frame df <-data.frame
#heterogeneous structure that includes the same number of objects

#read in dataframes
#df <- read.csv(
#file= path to file name
#sep=",",  #comma separated file
#header=TRUE 
#stringsAsFactors=FALSE)
```{r}
library(tidyverse)
reduced <- read_csv("~/reduced.csv", col_names = TRUE)
```


